Towards an open-source landscape for 3D CSEM modelling

### 2021-06-08 manuscript/Manuscript.tex
Point Zenodo to newest version

\section{Data}
The resulting CSEM responses of the four codes for the three models, as well as all files to rerun the different models with the four codes and reproduce the shown results are available at Zenodo (\href{https://doi.org/10.5281/zenodo.4535603}{10.5281/zenodo.4535603}).

>>>>

\section{Data}
The resulting CSEM responses of the four codes for the three models, as well as all files to rerun the different models with the four codes and reproduce the shown results are available at Zenodo (\href{https://doi.org/10.5281/zenodo.4535602}{10.5281/zenodo.4535602}).
